Human-Computer Mobile Distributed Computing for Time Series Forecasting\thanks{This work was supported with private funding by Velbazhd Software LLC.}

### 2019-09-24 Human-Computer-Mobile-Distributed-Computing-for-Time-Series-Forecasting/paper.tex
Small errors were fixed.

\author{
	Rumen Ketipov \and
	Georgi Kostadinov \and
	Plamen Petrov \and \\
	Iliyan Zankinskir \and
	Todor Balabanov\orcidID{0000-0003-3139-069X}
}
% Rumen Ketipov - rketipov@iit.bas.bg
% Georgi Kostadinov - g.kostadinov@iit.bas.bg
% Plamen Petrov - p.petrov@iit.bas.bg
% Iliyan Zankinski - iliyan@hsi.iccs.bas.bg
% Todor Balabanov - todorb@iinf.bas.bg

\authorrunning{R. Ketipov et al.}

>>>>

\author{
	Rumen Ketipov \and
	Georgi Kostadinov \and
	Plamen Petrov \and \\
	Iliyan Zankinski \and
	Todor Balabanov\orcidID{0000-0003-3139-069X}
}
% Rumen Ketipov - rketipov@iit.bas.bg
% Georgi Kostadinov - g.kostadinov@iit.bas.bg
% Plamen Petrov - p.petrov@iit.bas.bg
% Iliyan Zankinski - iliyan@hsi.iccs.bas.bg
% Todor Balabanov - todorb@iinf.bas.bg

\authorrunning{R. Ketipov et al.}
\titlerunning{Human-Computer MDC for TS Forecasting}
